Automating G\"odel's Ontological Proof of God's Existence with Higher-order Automated Theorem Provers

### 2014-05-19 Papers/2014-ECAI/ECAI-51.tex
added further minor modifications for the final version

A particular strength of our universal logic framework is that it can
be easily adapted for logic variations and even supports flexible
combinations of logics (cf.~\cite{C36}). In ongoing and future work we
will therefore investigate further logic parameters for G{\"o}del's
argument, including varying domains at higher types and non-rigid
terms. We plan to make the entire landscape of results available to
the interested theoretical philosophy and theology communities. This
is relevant, since philosophers are sometimes imprecise about the
very details of the logics they employ.

@@

\paragraph{Acknowledgments} This work has been supported by the German Research Foundation under grants BE 2501/9-1 and BE 2501/11-1. %We thank the anonymous reviewers for their comments and suggestions.

>>>>

A particular strength of our universal logic framework is that it can
be easily adapted for logic variations and even supports flexible
combinations of logics (cf.~\cite{C36}). In ongoing and future work we
will therefore investigate further logic parameters for G{\"o}del's
argument, including varying domains at higher types and non-rigid
terms. We plan to make the entire landscape of results available to
the interested
%theoretical philosophy and theology 
communities. This is relevant, since philosophers are sometimes
imprecise about the very details of the logics they employ.

@@

%\paragraph{Acknowledgments}
\section*{ACKNOWLEDGEMENTS}
 This work has been supported by the German Research Foundation under grants BE 2501/9-1 and BE 2501/11-1. %We thank the anonymous reviewers for their comments and suggestions.
